
Project: Weight Lifting Exercise Dataset
========================================================

## Introduction
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement - a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, my goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).


## Setting up Libraries and Loading the Data
```{r}
library(dplyr)
library(randomForest)
library(caret)

pmlTraining = read.csv(file = "./pml-training.csv", na.strings=c("", "NA"))
pmlTesting = read.csv(file = "./pml-testing.csv", na.strings=c("", "NA"))
```
## Explore the Features and Preprocessing
Because the testing file doesn't have the classes to test the data, the training file is divided into 70% training and 30% for the testing.
```{r}
set.seed(123)
inTrain = createDataPartition(pmlTraining$classe, p = 0.7, list = FALSE)
training = pmlTraining[inTrain, ]
testing = pmlTraining[-inTrain, ]
```
First check the ratio of NAs in each column in the training set and test set.
```{r}
table(colMeans(is.na(df.training)))
table(colMeans(is.na(df.testing)))
```
There are 67 columns in training set and 100 columns in test set with very high ratios of NAs. 

## Random Forest Prediction
Perform the random forest on the training data
```{r}
  modFit <- train(classe ~ num_window, method="rf", data= Rtraining, prox=TRUE)
}
```
It is found the result is a good fit.
```{r}
modFit
confusionMatrix(Rtesting$classe, predict(modFit, testing))
```
The confusion matrix indicates very low classification error, with a 1.2% out of bag error rate. 

## Testing the result
The trained random forest model is used to predict the testing data
```{r}
predict(modFit, testing)
```
## Reference
Velloso, E.; Bulling, A.; Gellersen, H.; Ugulino, W.; Fuks, H. Qualitative Activity Recognition of Weight Lifting Exercises. Proceedings of 4th International Conference in Cooperation with SIGCHI (Augmented Human '13) . Stuttgart, Germany: ACM SIGCHI, 2013. Read more: http://groupware.les.inf.puc-rio.br/har#wle_paper_section#ixzz3ALjBH6NX
http://www.stat.berkeley.edu/~breiman/RandomForests/cc_home.htm#ooberr

