
Project: Weight Lifting Exercise Dataset
========================================================

## Introduction
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement - a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, my goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).


## Setting up Libraries and Loading the Data
```{r}
library(dplyr)
library(randomForest)
library(caret)

pmlTraining = read.csv(file = "./pml-training.csv", na.strings=c("", "NA"))
pmlTesting = read.csv(file = "./pml-testing.csv", na.strings=c("", "NA"))
```
## Explore the Features and Preprocessing
Because the testing file doesn't have the classes to test the data, the training file is divided into 70% training and 30% for the testing.
```{r}
set.seed(123)
inTrain = createDataPartition(pmlTraining$classe, p = 0.7, list = FALSE)
training = pmlTraining[inTrain, ]
testing = pmlTraining[-inTrain, ]
```

Thirdly, By heuristic, I omited some the features that are marked redundant terms: X, time, user_name. I also looked at the data values quickly and found that:
  1. new_window is boolean variable so mabe it does not affect the classification
  2. A lot of fields have NA value or miss-value so I should choose some the meaningful variables for classification
  
Next, I removed the colums that have NA or miss-value
```{r}
index <- c()
n <- dim(training)[2]
for( i in 1:n){
  if(is.numeric(training[,i])  & is.numeric(testing[,i]) ){
    index <- c(index, i)
  }
}
index <- c(index, 160)
realTraing <- training[,index]

```
After that, I made some graphes the make me a overview from the data. The first variable that I chose is num_window
```{r}
library(caret)
par(mfcol=c(5,1))

ggplot(aes(num_window), data= training) +
  geom_histogram(aes(colour=classe, fill=classe), binwidth=1) +
  facet_wrap(~classe, ncol=1)
```

Then, Based on this graph, the evidence that is the distinct bin's values for each class is meaningfully. Thus, I try to test just attribute with a sepecific machine learning algorith. Based on my experince, I notice that the distribute the num_window value in a class does not continue so I chose the random forest algorithm.
Next step, make a validation set and testing set
```{r}
inTrain <- createDataPartition(y=training$classe,p=0.7, list=FALSE)
Rtraining <- training[inTrain,-1]
Rtesting <- training[-inTrain,-1]

```
Nextly, I run the random forest on Rtraing data
```{r}
if (file.exists("modFit2_rf_numwindow.RData")) {
    load("modFit2_rf_numwindow.RData")
} else {
  modFit2 <- train(classe ~ num_window, method="rf", data= Rtraining, prox=TRUE)
  save(modFit2, file = "modFit2_rf_numwindow.RData")
}
```
Waiting some minutes for completing, I found the result that is very best fit
```{r}
modFit2
confusionMatrix(Rtesting$classe, predict(modFit2, Rtesting))
```
Finally,I used this model for predicting on the testing data
```{r}
predict(modFit2, testing)
```



